The \dealii{} Library, Version 9.2

### 2020-06-03 9.2/paper.tex
add todo
fix support for Timo, Conrad, and Wolfgang

\dealii{} can interface with many other libraries:
\todo[inline]{We picked up gingko. Anything else?}
\begin{multicols}{3}
  \begin{itemize}
    \item ADOL-C \cite{Griewank1996a,adol-c}
    \item ARPACK \cite{arpack}
    \item Assimp \cite{assimp}
    \item BLAS and LAPACK \cite{lapack}
    \item cuSOLVER \cite{cusolver}
    \item cuSPARSE \cite{cusparse}
    \item Gmsh \cite{geuzaine2009gmsh}
    \item GSL \cite{gsl2016}
    \item Ginkgo \cite{ginkgo-web-page}
    \item HDF5 \cite{hdf5}
    \item METIS \cite{karypis1998fast}
    \item MUMPS \cite{ADE00,MUMPS:1,MUMPS:2,mumps-web-page}
    \item muparser \cite{muparser-web-page}
    \item nanoflann \cite{nanoflann}
          %
          % nanoflann has been deprecated and will be removed for 9.3. remove
          % this line in the 9.3 release paper
          %
    \item NetCDF \cite{rew1990netcdf}
          %
          % netcdf has been deprecated and will be removed for 9.3. remove
          % this line in the 9.3 release paper
          %
    \item OpenCASCADE \cite{opencascade-web-page}
    \item p4est \cite{p4est}
    \item PETSc \cite{petsc-user-ref,petsc-web-page}
    \item ROL \cite{ridzal2014rapid}
    \item ScaLAPACK \cite{slug}
    \item SLEPc \cite{Hernandez:2005:SSF}
    \item SUNDIALS \cite{sundials}
    \item SymEngine \cite{symengine-web-page}
    \item TBB \cite{Rei07}
    \item Trilinos \cite{trilinos,trilinos-web-page}
    \item UMFPACK \cite{umfpack}
  \end{itemize}
\end{multicols}
Please consider citing the appropriate references if you use interfaces to these
libraries.

@@

W.~Bangerth, T.~C.~Clevenger, and T.~Heister were partially
supported by the National Science Foundation under award OAC-1835673
as part of the Cyberinfrastructure for Sustained Scientific Innovation (CSSI)
program  and by the Computational Infrastructure
in Geodynamics initiative (CIG), through the National Science
Foundation under Award No.~EAR-1550901 and The
University of California -- Davis.

\todo[inline]{Timo needs to fix his support}

W.~Bangerth and T.~Heister were also partially supported by award DMS-1821210
and EAR-1925595.

@@

@@

T.~Heister was also partially supported by NSF Award DMS-1522191, and
by Technical Data Analysis, Inc. through US Navy SBIR N16A-T003.

@@

>>>>

\dealii{} can interface with many other libraries:
\todo[inline]{We picked up gingko. Anything else?}
\todo[inline]{Timo says: should we remove deprecated modules already? (nanoflann, netcdf)}
\begin{multicols}{3}
  \begin{itemize}
    \item ADOL-C \cite{Griewank1996a,adol-c}
    \item ARPACK \cite{arpack}
    \item Assimp \cite{assimp}
    \item BLAS and LAPACK \cite{lapack}
    \item cuSOLVER \cite{cusolver}
    \item cuSPARSE \cite{cusparse}
    \item Gmsh \cite{geuzaine2009gmsh}
    \item GSL \cite{gsl2016}
    \item Ginkgo \cite{ginkgo-web-page}
    \item HDF5 \cite{hdf5}
    \item METIS \cite{karypis1998fast}
    \item MUMPS \cite{ADE00,MUMPS:1,MUMPS:2,mumps-web-page}
    \item muparser \cite{muparser-web-page}
    \item nanoflann \cite{nanoflann}
          %
          % nanoflann has been deprecated and will be removed for 9.3. remove
          % this line in the 9.3 release paper
          %
    \item NetCDF \cite{rew1990netcdf}
          %
          % netcdf has been deprecated and will be removed for 9.3. remove
          % this line in the 9.3 release paper
          %
    \item OpenCASCADE \cite{opencascade-web-page}
    \item p4est \cite{p4est}
    \item PETSc \cite{petsc-user-ref,petsc-web-page}
    \item ROL \cite{ridzal2014rapid}
    \item ScaLAPACK \cite{slug}
    \item SLEPc \cite{Hernandez:2005:SSF}
    \item SUNDIALS \cite{sundials}
    \item SymEngine \cite{symengine-web-page}
    \item TBB \cite{Rei07}
    \item Trilinos \cite{trilinos,trilinos-web-page}
    \item UMFPACK \cite{umfpack}
  \end{itemize}
\end{multicols}
Please consider citing the appropriate references if you use interfaces to these
libraries.

@@

W.~Bangerth, T.~C.~Clevenger, and T.~Heister were partially
supported by the Computational Infrastructure
in Geodynamics initiative (CIG), through the National Science
Foundation under Award No.~EAR-1550901 and The
University of California -- Davis.

W.~Bangerth was also partially supported by award OAC-1835673 as part of the Cyberinfrastructure for Sustained Scientific Innovation (CSSI)
program, DMS-1821210,
and EAR-1925595.

@@

T.~C.~Clevenger was also partially supported EAR-1925575 and OAC-2015848.

@@

Timo Heister was also partially supported by the National Science Foundation (NSF)
Award DMS-2028346, OAC-2015848, EAR-1925575, and by
Technical Data Analysis, Inc. through US Navy STTR Contract N68335-18-C-0011.

@@

Clemson University is acknowledged for generous allotment of compute time on Palmetto cluster.
